Behind Bars and Beyond: Investigating Socioeconomic Drivers of Incarceration Rates in the United States

### 2024-04-19 paper/paper.qmd
Minor amendments to subheaders
Added shiny app.

---
title: "Behind Bars and Beyond: Investigating Socioeconomic Drivers of Incarceration Rates in the United States"
subtitle: "A comparative analysis of global trends and America's mass incarceration crisis."
author: 
  - Abbass Sleiman
thanks: "Code and data are available at: [https://github.com/AbbassSleiman/US-Middle-Class](https://github.com/AbbassSleiman/US-Middle-Class)."
date: today
date-format: long
format: 
  pdf: 
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
    documentclass: article
    geometry: margin = 1.2in
    abstract: "Over the last 2 decades, the United States has found itself struggling with an issue of mass incarceration, leading the world in number of individuals incarcerated. This paper investigates the possible causes of this by conducting a comparative analysis of global trends in education, unemployment, crime, and poverty rates, and their respective impacts on incarceration. Utilizing data from the World Population Review, and employing a Bayesian multiple linear regression model, this paper finds evidence that poverty and unemployment negatively correlate with incarceration rates, whereas violent crime rates positively correlate. The paper also identifies nuances in the relationship between educational attainment and incarceration rates. These insights may offer valuable considerations for policy-making aimed at addressing mass incarceration in the United States."
    number-sections: true
output: 
  bookdown::pdf_document2
toc: true
bibliography: references.bib
---

@@

# Package loading
library(tidyverse)
library(here)
library(ggplot2)
library(knitr)
library(modelsummary)
library(rstanarm)
library(kableExtra)
library(dplyr)
library(janitor)

@@

All data analysis was done through R [@citeR] with the aid of the following packages: `tidyverse` [@citetidyverse], `here` [@citehere], `ggplot2` [@citeggplot2], `knitr` [@citeknitr], `modelsummary` [@citemodelsummary], `rstanarm` [@citerstanarm], `kableExtra` [@citekableExtra], `dplyr` [@citedplyr], and `janitor` [@citejanitor].

@@

## Posterior predictive check

@@

## Comparison of the posterior and prior

>>>>

---
title: "Behind Bars and Beyond: Investigating Socioeconomic Drivers of Incarceration Rates in the United States"
subtitle: "A comparative analysis of global trends and America's mass incarceration crisis."
author: 
  - Abbass Sleiman
thanks: "Code and data are available at: [https://github.com/AbbassSleiman/US-Middle-Class](https://github.com/AbbassSleiman/US-Middle-Class). Shiny webapp can be accessed at []()"
date: today
date-format: long
format: 
  pdf: 
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
    documentclass: article
    geometry: margin = 1.2in
    abstract: "Over the last 2 decades, the United States has found itself struggling with an issue of mass incarceration, leading the world in number of individuals incarcerated. This paper investigates the possible causes of this by conducting a comparative analysis of global trends in education, unemployment, crime, and poverty rates, and their respective impacts on incarceration. Utilizing data from the World Population Review, and employing a Bayesian multiple linear regression model, this paper finds evidence that poverty and unemployment negatively correlate with incarceration rates, whereas violent crime rates positively correlate. The paper also identifies nuances in the relationship between educational attainment and incarceration rates. These insights may offer valuable considerations for policy-making aimed at addressing mass incarceration in the United States."
    number-sections: true
output: 
  bookdown::pdf_document2
toc: true
bibliography: references.bib
---

@@

# Package loading
library(tidyverse)
library(here)
library(ggplot2)
library(knitr)
library(modelsummary)
library(rstanarm)
library(kableExtra)
library(dplyr)
library(janitor)
library(shiny)

@@

All data analysis was done through R [@citeR] with the aid of the following packages: `tidyverse` [@citetidyverse], `here` [@citehere], `ggplot2` [@citeggplot2], `knitr` [@citeknitr], `modelsummary` [@citemodelsummary], `rstanarm` [@citerstanarm], `kableExtra` [@citekableExtra], `dplyr` [@citedplyr], and `janitor` [@citejanitor]. Moreover, the shiny web app associated with this paper was made with the aid of the `shiny` package [@citeshiny].

@@

## Posterior Predictive Check

@@

## Comparison of the Posterior and Prior
